---
title: "Introduction to EasyMultiProfiler"
author: |
  | Bingdong Liu and Erqiang Hu
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: vignette
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to EasyMultiProfiler}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE, results="asis", message=FALSE, KnitrSetUp}
library(knitr)
knit_hooks$set(crop = hook_pdfcrop)
knitr::opts_chunk$set(crop = TRUE, tidy=FALSE, warning=FALSE,message=FALSE, fig.align="center")
Biocpkg <- function (pkg){
    sprintf("[%s](http://bioconductor.org/packages/%s)", pkg, pkg)
}

CRANpkg <- function(pkg){
    cran <- "https://CRAN.R-project.org/package" 
    fmt <- "[%s](%s=%s)"
    sprintf(fmt, pkg, cran, pkg) 
}
```

```{r, echo=FALSE, results="hide", message=FALSE, Loadpackages}
library(EasyMultiProfiler)
```

# 1. Introduction
The EasyMultiProfiler package aims to offer a user-friendly and efficient multi-omics data analysis tool on the R platform. It facilitates various essential tasks related to microbiome, genome, and metabolite downstream analysis, providing a seamless workflow from start to finish.

# 2. Function exhibition

## Supported Analysis
For more detailed information
```{r, warning=FALSE, message=FALSE}
help("EasyMultiProfiler")
```

+ Data Extract
  * EMP_assay_extract
  * EMP_coldata_extract
  * EMP_rowdata_extract
+ Data Preparation
  * EMP_adjust_abudance
  * EMP_collapse
  * EMP_decostand
  * EMP_feature_convert
  * EMP_impute
  * EMP_identify_assay
  * EMP_modify_assay
  * EMP_rrarefy
+ Data Analysis
  * EMP_alpha_analysis
  * EMP_cluster_analysis
  * EMP_cor_analysis
  * EMP_diff_analysis
  * EMP_dimension_analysis
  * EMP_enrich_analysis
  * EMP_marker_analysis
  * EMP_GSEA_analysis
  * EMP_WGCNA_cluster_analysis
  * EMP_WGCNA_cor_analysis
  * EMP_multi_analysis
+ Data Virtualization
  * EMP_boxplot
  * EMP_scatterplot
  * EMP_dotplot
  * EMP_netplot
  * EMP_curveplot
  * EMP_heatmap_plot
  * EMP_volcanol_plot
+ Data support
  * EMP_filter
  * EMP_history
  * EMP_result
  * EMP_summary
  * EMP_taxonomy_import
  * EMP_function_import
  * EMP_normal_import
  * EMP_easy_import

# Vignette

Please go to <https://github.com/liubingdong/EasyMultiProfiler/tree/main> for the full vignette.










